|

### 2022-03-15 manuscript/manuscript_1.0.Rmd
new file with notes of to-dos. Small changes in the manuscript

---
title: |
  | Learning can mediate both badges of status and individual recognition
author:
- Andrés E. Quiñones^[Laboratorio de Biología Evolutiva de Vertebrados, Departamento
  de Ciencias Biológicas, Universidad de los Andes, Bogotá, Colombia]
- C. Daniel Cadena*
- Olof Leimar^[Department of Zoology, Stockholm University, Stockholm, Sweden]
- Redouan Bshary^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland]
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  word_document: default
fig_caption: yes
fontsize: 12pt
header-includes:
- \usepackage{float}
- \usepackage{setspace}\doublespacing
- \linespread{2}
- \usepackage{lineno}
- \linenumbers
- \floatplacement{figure}{H}
keep_tex: yes
keywords: My keywords
linespread: 2
bibliography: ../SocialMorphCue.bib
spacing: double
style: C:\Users\andre\Zotero\styles\elife.csl
abstract: Adaptive behavioural responses often depend on qualities of the interacting partner of an individual. For example, when competing for resources, an individual might be better off escalating fights with individuals of lower quality, while restraining from fighting individuals of higher quality. Communication systems involving signals of quality allow individuals to reduce uncertainty regarding the fighting ability of their partners and make more adaptive behavioral decisions. However, dishonest individuals can destabilize such communications systems. One open question is whether cognitive mechanisms, such as learning, can maintain the honesty of signals, thus, favoring their evolutionary stability. Here we present evolutionary simulations, where individuals can produce a signal proportional to their quality; and learn along their lifetime the best response to the signal emitted by their peers. In these simulations, learning on the receiver side can mediate the evolution of signals of quality on the sender side. When the cost of the signal is proportional to the quality of the sender populations are only composed of honest signalers. When the cost is not proportional to the quality of the signaler, the population is composed of both honest and dishonest signalers. We argue that learning can be a general cognitive mechanism playing a role in a wide range of communication systems.  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(png)
require(here)
source(here("../R_files/posPlots.r"))
source(here("AccFunc.r"))
```

@@

The outcome of interactions with con-specifics is an important 
determinant of fitness in social animals. Irrespective of whether such interactions are cooperative 
or competitive, the actions of interacting individuals partly determine 
their reproductive success. However, the best action for an individual 
might vary depending on its condition, and that of individuals with whom it interacts. 
Thus, acting based on information about interacting 
partners is typically adaptive [@quinones_Negotiation_2016].
Acquiring this information, however, is far from trivial. 
In some cases, interacting partners (signallers) might be 'willing' to provide accurate
information, but in others it might be in their own interest to conceal information
[@johnstone_Recognition_1997], or to provide erroneous information [@johnstone_Badges_1993]. 
Typically, in a given context, some proportion of individuals will benefit 
from broadcasting accurate information, whereas others will benefit from hiding it. 
Take, for instance, an interaction between two individuals where one can help the other. 
Given some costs and benefits, a potential donor will be interested in helping 
related individuals. Therefore, for a relative of the donor, 
broadcasting kinship is advantageous, whereas for an unrelated individual, 
concealing the lack of kinship is better. Similar scenarios may apply to 
many aspects of social life such as finding mates, feeding offspring, dominance relationships 
and aggressive interactions [@bradbury_Principles_2011; @moller_Female_1988; @tibbetts_Socially_2004].
In dominance and aggressive interactions, an important piece of
information to guide individual actions is interacting partners fighting ability, 
which is sometimes referred to as Resource Holding Potential (RHP) [@parker_Assessment_1974], 
or simply as quality. Responsiveness to the quality of the 
partner is central to communication systems such as badges of status, 
where an arbitrary signal conveys quality [@johnstone_Badges_1993; @rohwer_Social_1975a]. 
Here, arbitrary refers to a signal which is not ontogenetically correlated with quality. 
Badges of status can be evolutionarily stable whenever the signal imposes a fitness cost which 
decreases with the quality of an individual  [@botero_Evolution_2010; @johnstone_Badges_1993], 
such that it's no longer in the interest of low quality individuals to fake quality by producing a
large badge. The cost of honest signals is a more general principle of communications systems, 
usually referred to as the handicap principle [@grafen_Biological_1990; @zahavi_Mate_1975]. 
An alternative system of communication is one where individuals gather and store information
about each individual they interact with. This information should reliably allow 
each individual to react adaptively to the quality difference with their opponent. 
This type of assessment strategy is often referred to as individual recognition [@whitfield_Plumage_1986]. Evidently, individual recognition is restricted to 
certain interaction structures, because individuals are limited by cognitive 
abilities in how many individuals they can recognize and track. Thus, individual 
recognition and badges of status have been assumed to be alternative communication 
systems fulfilling the same function, reducing the costs of aggression in contests over resources. 
Furthermore, badges of status and individual recognition are expected to evolve under different interaction structures, badges of status under global interactions and individual recognition
under local interactions [@dale_Signaling_2001; @sheehan_There_2016].  There is no clear cut reason, however, why both systems could not work together, in fact there is some evidence
that they can [@chaine_Manipulating_2018].

@@

We model the evolution of signals of quality in the context of agonistic interactions by 
modelling a population of haploid individuals with non-overlapping generations. 
Individuals are born every generation with a level of quality ($Q_i$, where $i$ is subscript 
of the population vector of size $N$) given by a number between zero and one, which is drawn 
from a truncated normal distribution $N(\mu = 0.5,\sigma)$. 
An individual with quality $0$ has the lowest RHP, 
while an individual with quality $1$ has the highest. As part of development processes
individuals produce a morphological signal (badge), the size of such depends on their level 
of quality according to a reaction norm given by $B_i=1/(1+e^{\alpha_i-\beta_i Q_i})$;
where are $\alpha_i$ and $\beta_i$ are individual specific traits that determine 
the shape of the reaction norm (Fig. \ref{fig:model-struc} A). Variation in $\alpha_i$ and $\beta_i$ means individuals can have either uninformative (flat) or informative (logistic) norms. 
The size of the signal is constrained between zero and one. We assume different values of these traits 
are given by different alleles, and are inherited from mother to offspring. 
Unless, with a small probability, mutation changes the allelic value of the offspring.
After birth individuals go through a round of viability selection. 
Individual specific survival probability is given by $s_i=1/(1+e^{-k_1-k_2(Q_i-B_i)})$. 
Where $k_1$ and $k_2$ are parameter values determining the shape of the survival function. 
Importantly, if $k_2=0$ survival probability is independent of quality, while if $k_2>0$
lower quality individuals pay a higher price for s similar-sized badge, fulfilling the core assumption 
of the handicap principle [@botero_Evolution_2010; @grafen_Biological_1990; @johnstone_Badges_1993].

Individuals who survive engage in a series of pairwise interactions 
where they compete for resources. Individuals in real populations typically do not 
interact at random nor with all individuals in the population [@kurvers_Evolutionary_2014]. 
In order to allow for non-random interactions, we use the population vector to define 
an interaction neighbourhood for the focal individual, the size of the neighbourhood (g) 
is the number of positions around the focal's from which the interactant is drawn. 
So, if $g=N$ interactions are global; as $g$ gets smaller interactions are more local. 
In an interaction each individual must decide whether to escalate a fight or not. 
Following the classic hawk-dove game [@maynard-smith_Evolution_1982], if the focal individual fights and its partner does not, the focal gets as pay-off the resource of value $V$ while its partner gets nothing; if both individuals restrain  from fighting they split up the resource in half; if both decide to fight they split up the cost of fighting and the winner takes over the resource. 
We further assume that the probability of wining a fight for the focal individual depends on the difference in quality between her and her interacting partner; specifically it is given by $p_{ij}=1/(1+e^{-k_3(Q_i-Q_j)})$, where $k_3$ is a parameter defining
how strong the quality difference determines the winning probability; 
and $i$ and $j$ denote the the position in the population 
vector of the focal and its interacting partner respectively.

The decision of whether to escalate a fight against an interacting partner can be dependent 
on the size of the partner's badge, the actual dependency is determined by 
the focal´s experiences through a learning process. We implement learning using 
the actor-critic approach from reinforcement learning theory [RL; @sutton_Reinforcement_2018;@quinones_Reinforcement_2019; @leimar_Learning_2019].
Individuals estimate the reward (pay-off) expected from  interacting with partners 
of different badge sizes (the critic in RL terminology). 
After every interaction they update the estimate of reward proportionally to the difference between their current estimate and the observed reward (prediction error $\delta$) and to 
the speed of learning ($\mathrm{A}$).
Furthermore, they express different probabilities of retreating (attacking) depending on
the badge size of their opponent (the actor in RL). They update the probability of 
retreating (attacking)  up or down depending on whether retreating (attacking) leads to an increase 
in the reward estimation. So, if a focal individual decides to escalate a fight against 
an individual with small badge, and that leads to an increase in the reward estimation,
the focal individual will increase the probability of escalating fights with 
individuals of small badges in the future. Given that badge size is a real number between 0 and 1, there are infinitely many badge sizes. Thus, the reward estimation, as well as the probability of retreating (escalating), must be generalized across different values. 
To implement generalization we use the linear function
approximation method based on radial basis functions [@sutton_Reinforcement_2018]. Specifically, we pick $c$ feature centres, which are evenly spaced values along the badge size interval ([0,1]). Each one of these features centres is associated with a weight for reward estimation and 
tendency to play retreat in a given interaction. The reward estimation and the tendency 
to retreat are calculated (in every interaction) as the sum of the weights associated 
with each feature, weighted by the response triggered by the feature 
(Fig. \ref{fig:model-struc} B, dots represent the feature weights) 
The response of each feature centre diminishes as a Gaussian function  with the distance between the feature centre and the badge size of the partner (Fig. \ref{fig:model-struc} B, grey line). Formally the reward estimation 
$\hat{R}$ when the focal individual ($i$) faces individual $j$ is given by,

\begin{equation}
\hat{R}_{ij} =  \sum_{z=1}^{c} x_z e^{(-\frac{|B_i-c_z|}{2\theta^2})} 
\end{equation}

@@

extSimsDir<-paste0("e:/BadgeSims/",scenario1,"_")
listTest<-list.files(extSimsDir,full.names = TRUE)
indList<-grep("ind",listTest,value=TRUE)
# parameter values from project folder
paramName<-list.files(here("Simulations",paste0(scenario1,"_")))
# paramName<-list.files(extSimsDir,full.names = TRUE)
paramName<-grep(".json",paramName,value=TRUE)
param<-fromJSON(here("Simulations",paste0(scenario1,"_"),paramName[2]))
# fromJSON(paramName[1])
fileId<-1 # choose the replicate

@@

extSimsDir<-paste0("e:/BadgeSims/",scenario2,"_")
listTest<-list.files(extSimsDir,full.names = TRUE)
indList<-grep("ind",listTest,value=TRUE)
# parameter values from project folder
paramName<-list.files(here("Simulations",paste0(scenario1,"_")))
# paramName<-list.files(extSimsDir,full.names = TRUE)
paramName<-grep(".json",paramName,value=TRUE)
param<-fromJSON(here("Simulations",paste0(scenario1,"_"),paramName[2]))
# fromJSON(paramName[1])
fileId<-1 # choose the replicate

@@

When production of the badge is not costly (i.e. does not work as a handicap), the parameters of the sender code go through evolutionary branching event, triggereing the evolution of different types of
signals in the population. Fig. \ref{fig:branching}A and B shows changes in the distribution of the 
sender reaction norm ($\alpha$ and $\beta$) along evolutionary time. Darker areas show trait values 
with high frequency in the population. Populations start monomorphic with a value of zero on both traits, and mutations quickly buid up a normal distribution around the starting value. Within the first 2000 generations the unimodal distribution splits into a bimodal one. In the case of $\alpha$, one of the peaks splits further, so at the end of the evolutionary simulation the distribution of $\alpha$ value in the population shows three peaks. In the case of $\beta$, the two initial peaks coexist for around 4000 generations. Later on one of the types goes extinct and the distribution goes back to being unimodal. These changes in the distrubtuion of the sender reaction norm parameters imply that during the second half of the simualation individuals can by classify into three distinct types. Two types express a flat reaction norm, meaning that their badge size is not informative of their quality, while the third type shows intermediate badge sizes which are determined by the quality of the individual (Fig. \ref{fig:branching}). Furthermore, the receiver reaction norms develop through learning, particularly those of individuals of intermediate quality, respond to the signal of their sender type by increasing the probability of retreating from a fight with individuals with larger badges (Fig. \ref{fig:branching}).

>>>>

---
title: |
  | Learning can mediate both badges of status and individual recognition
author:
- Andrés E. Quiñones^[Laboratorio de Biología Evolutiva de Vertebrados, Departamento
  de Ciencias Biológicas, Universidad de los Andes, Bogotá, Colombia]
- C. Daniel Cadena*
- Olof Leimar^[Department of Zoology, Stockholm University, Stockholm, Sweden]
- Redouan Bshary^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland]
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  word_document: default
fig_caption: yes
fontsize: 12pt
header-includes:
- \usepackage{float}
- \usepackage{setspace}\doublespacing
- \linespread{2}
- \usepackage{lineno}
- \linenumbers
- \floatplacement{figure}{H}
keep_tex: yes
keywords: My keywords
linespread: 2
bibliography: ../SocialMorphCue.bib
spacing: double
style: C:\Users\andre\Zotero\styles\elife.csl
abstract: | 
  Adaptive behavioural responses often depend on qualities of the interacting partner of an individual. For example, when competing for resources, an individual might be better off escalating fights with individuals of lower quality, while restraining from fighting individuals of higher quality. Communication systems involving signals of quality allow individuals to reduce uncertainty regarding the fighting ability of their partners and make more adaptive behavioral decisions. However, dishonest individuals can destabilize such communications systems. One open question is whether cognitive mechanisms, such as learning, can maintain the honesty of signals, thus, favoring their evolutionary stability. Here we present evolutionary simulations, where individuals can produce a signal proportional to their quality; and learn along their lifetime the best response to the signal emitted by their peers. In these simulations, learning on the receiver side can mediate the evolution of signals of quality on the sender side. When the cost of the signal is proportional to the quality of the sender populations are only composed of honest signalers. When the cost is not proportional to the quality of the signaler, the population is composed of both honest and dishonest signalers. We argue that learning can be a general cognitive mechanism playing a role in a wide range of communication systems.  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache=TRUE)
require(png)
require(here)
source(here("../R_files/posPlots.r"))
source(here("AccFunc.r"))
```

@@

The outcome of interactions with con-specifics is an important 
determinant of fitness in social animals. Irrespective of whether 
such interactions are cooperative or competitive, the actions of 
interacting individuals partly determine 
their reproductive success. However, the best action for an individual 
might vary depending on its condition, and that of individuals with 
whom it interacts. Thus, acting based on information about interacting 
partners is typically adaptive [@quinones_Negotiation_2016].
Acquiring this information, however, is far from trivial. 
In some cases, interacting partners (signallers) might be 'willing' to 
provide accurate information, but in others it might be in their 
own interest to conceal information [@johnstone_Recognition_1997], 
or to provide erroneous information [@johnstone_Badges_1993]. 
Typically, in a given context, some proportion of individuals will benefit 
from broadcasting accurate information, whereas others will benefit 
from hiding it. Take, for instance, an interaction between two individuals 
where one can help the other. Given some costs and benefits, 
a potential donor will be interested in helping 
related individuals. Therefore, for a relative of the donor, 
broadcasting kinship is advantageous, whereas for an unrelated individual, 
concealing the lack of kinship is better. Similar scenarios may apply to 
many aspects of social life such as finding mates, 
feeding offspring, dominance relationships and aggressive interactions 
[@bradbury_Principles_2011; @moller_Female_1988; @tibbetts_Socially_2004].
In dominance and aggressive interactions, an important piece of
information to guide individual actions is interacting 
partners fighting ability, which is sometimes referred to as 
Resource Holding Potential (RHP) 
[@parker_Assessment_1974], or simply as quality. 
Responsiveness to the quality of the partner is central 
to communication systems such as badges of status, 
where an arbitrary signal conveys quality 
[@johnstone_Badges_1993; @rohwer_Social_1975a]. 
Here, arbitrary refers to a signal which is not 
ontogenetically correlated with quality. 
Badges of status can be evolutionarily stable whenever the 
signal imposes a fitness cost which decreases with the 
quality of an individual  [@botero_Evolution_2010; @johnstone_Badges_1993], 
such that it's no longer in the interest of low quality individuals 
to fake quality by producing a large badge. The cost of honest signals 
is a more general principle of communications systems, 
usually referred to as the handicap principle 
[@grafen_Biological_1990; @zahavi_Mate_1975]. 
<!-- should this last part of the paragraph stay ?-->
An alternative system of communication is one where individuals 
gather and store information about each individual they interact with. 
This information should reliably allow each individual to react adaptively 
to the quality difference with their opponent. This type of 
assessment strategy is often referred to as individual 
recognition [@whitfield_Plumage_1986]. Evidently, individual recognition 
is restricted to  certain interaction structures, because individuals 
are limited by cognitive abilities in how many individuals 
they can recognize and track. Thus, individual recognition and 
badges of status have been assumed to be alternative communication 
systems fulfilling the same function, reducing the costs of 
aggression in contests over resources.

Furthermore, badges of status and individual recognition are expected 
to evolve under different interaction structures, badges of status under 
global interactions and individual recognition
under local interactions [@dale_Signaling_2001; @sheehan_There_2016].  
There is no clear cut reason, however, why both systems could not 
work together, in fact there is some evidence
that they can [@chaine_Manipulating_2018].

@@

We model the evolution of signals of quality in the context of agonistic 
interactions. For simplicity we consider a population of haploid 
individuals with non-overlapping generations. Individuals are born 
every generation with a level of quality ($Q_i$, where $i$ is subscript 
of the population vector of size $N$) given by a number between zero and one, 
which is drawnfrom a truncated normal distribution 
$N(\mu = 0.5,\sigma)$. An individual with quality $0$ has the lowest RHP, 
while an individual with quality $1$ has the highest. As part of 
development processes individuals produce a morphological signal (badge), 
the size of such depends on their level 
of quality according to a reaction norm given by 
$B_i=1/(1+e^{\alpha_i-\beta_i Q_i})$; where are $\alpha_i$ and 
$\beta_i$ are individual specific traits that determine the shape of 
the reaction norm (Fig. \ref{fig:model-struc} A). Variation in $\alpha_i$ 
and $\beta_i$ means individuals can have either uninformative (flat) or 
informative (logistic) norms. The size of the signal is constrained 
between zero and one. We assume different values of these traits 
are given by different alleles, and are inherited from mother to offspring. 
Unless, with a small probability, mutation changes the allelic value 
of the offspring. After birth individuals go through a round of 
viability selection. Individual specific survival probability is given by $s_i=1/(1+e^{-k_1-k_2(Q_i-B_i)})$. Where $k_1$ and $k_2$ are parameter 
values determining the shape of the survival function. 
Importantly, if $k_2=0$ survival probability is independent of quality, 
while if $k_2>0$ lower quality individuals pay a higher price for similar-sized 
badge, fulfilling the core assumption of the handicap principle 
[@botero_Evolution_2010; @grafen_Biological_1990; @johnstone_Badges_1993].

Individuals who survive engage in a series of pairwise interactions 
where they compete for resources. Individuals in real populations typically 
do not interact at random nor with all individuals in the population 
[@kurvers_Evolutionary_2014]. In order to allow for non-random interactions, 
we use the population vector to define an interaction neighbourhood 
for the focal individual, the size of the neighbourhood ($g$)
is the number of positions around the focal's from which the partner is drawn. 
So, if $g=N$ interactions are global; as $g$ gets smaller 
interactions are more local. In an interaction each individual must 
decide whether to escalate a fight or not. 
Following the classic *hawk-dove* game [@maynard-smith_Evolution_1982], 
if the focal individual fights and its partner does not, the focal gets 
as pay-off the resource of value $V$ while its partner gets nothing; 
if both individuals restrain  from fighting they split up the resource 
in half; if both decide to fight they split up the cost of fighting and 
the winner takes over the resource. We further assume that the 
probability of wining a fight for the focal individual depends on the 
difference in quality between her and her interacting partner; specifically 
it is given by $p_{ij}=1/(1+e^{-k_3(Q_i-Q_j)})$, where $k_3$ is a 
parameter defining how strong the quality difference determines the 
winning probability; and $i$ and $j$ denote the the position 
in the population vector of the focal and its interacting 
partner respectively.

The decision of whether to escalate a fight against an interacting 
partner can be dependent on the size of the partner's badge, 
the actual dependency is determined by the focal´s experiences 
through a learning process. We implement learning using 
the actor-critic approach from reinforcement learning theory [RL; @sutton_Reinforcement_2018;@quinones_Reinforcement_2019; @leimar_Learning_2019].
Individuals estimate the reward (pay-off) expected from  interacting 
with partners of different badge sizes (the critic in RL terminology). 
After every interaction they update the estimate of reward proportionally 
to the difference between their current estimate and the observed 
reward (prediction error $\delta$) and to the speed of learning 
($\mathrm{A}$). Furthermore, they express different probabilities of 
retreating (attacking) depending on the badge size of their opponent 
(the actor in RL). They update the probability of 
retreating (attacking)  up or down depending on whether retreating 
(attacking) leads to an increase in the reward estimation. 
So, if a focal individual decides to escalate a fight against 
an individual with small badge, and that leads to an increase in 
the reward estimation, the focal individual will increase the probability 
of escalating fights with individuals of small badges in the future. 
Given that badge size is a real number between 0 and 1, there are infinitely 
many badge sizes. Thus, the reward estimation, as well as the probability 
of retreating (escalating), must be generalized across different values. 
To implement generalization we use the linear function approximation 
method based on radial basis functions [@sutton_Reinforcement_2018]. 
Specifically, we pick $c$ feature centres, which are evenly spaced values 
along the badge size interval ([0,1]). Each one of these features centres 
is associated with a weight for reward estimation and tendency to play 
retreat in a given interaction. The reward estimation and the tendency 
to retreat are calculated (in every interaction) as the sum of the weights 
associated with each feature, weighted by the response 
triggered by the feature (Fig. \ref{fig:model-struc} B, dots 
represent the feature weights) The response of each feature centre 
diminishes as a Gaussian function  with the distance between the 
feature centre and the badge size of 
the partner (Fig. \ref{fig:model-struc} B, grey line). Formally the 
reward estimation $\hat{R}$ when the focal individual ($i$) faces 
individual $j$ is given by,
\
\begin{equation}
\hat{R}_{ij} =  \sum_{z=1}^{c} x_z e^{(-\frac{|B_i-c_z|}{2\theta^2})} 
\end{equation}

@@

extSimsDir<-paste0("M:/BadgeSims/",scenario1,"_")
listTest<-list.files(extSimsDir,full.names = TRUE)
indList<-grep("ind",listTest,value=TRUE)
# parameter values from project folder
paramName<-list.files(here("Simulations",paste0(scenario1,"_")))
# paramName<-list.files(extSimsDir,full.names = TRUE)
paramName<-grep(".json",paramName,value=TRUE)
param<-fromJSON(here("Simulations",paste0(scenario1,"_"),paramName[2]))
# fromJSON(paramName[1])
fileId<-1 # choose the replicate

@@

extSimsDir<-paste0("M:/BadgeSims/",scenario2,"_")
listTest<-list.files(extSimsDir,full.names = TRUE)
indList<-grep("ind",listTest,value=TRUE)
# parameter values from project folder
paramName<-list.files(here("Simulations",paste0(scenario1,"_")))
# paramName<-list.files(extSimsDir,full.names = TRUE)
paramName<-grep(".json",paramName,value=TRUE)
param<-fromJSON(here("Simulations",paste0(scenario1,"_"),paramName[2]))
# fromJSON(paramName[1])
fileId<-1 # choose the replicate

@@

When production of the badge is not costly (i.e. does not work as a handicap), 
the parameters of the sender code go through evolutionary branching event, 
triggering the evolution of different types of signals in the population. 
Fig. \ref{fig:branching}A and B shows changes in the distribution of the 
sender reaction norm ($\alpha$ and $\beta$) along evolutionary time. 
Darker areas show trait values with high frequency in the population. 
Populations start monomorphic with a value of zero on both traits, 
and mutations quickly build up a normal distribution around the starting 
value. Within the first 2000 generations the unimodal distribution splits 
into a bimodal one. In the case of $\alpha$, one of the peaks splits further, 
so at the end of the evolutionary simulation the distribution of $\alpha$ 
value in the population shows three peaks. In the case of $\beta$, the two 
initial peaks coexist for around 4000 generations. Later on one of the 
types goes extinct and the distribution goes back to being unimodal. 
These changes in the distribution of the sender reaction norm parameters 
imply that during the second half of the simulation individuals can be 
classified into three distinct types. Two types express a flat reaction 
norm, meaning that their badge size is not informative of their quality, 
while the third type shows intermediate badge sizes which are determined 
by the quality of the individual (Fig. \ref{fig:branching}). Furthermore, 
the receiver reaction norms develop through learning, particularly those 
of individuals of intermediate quality, respond to the signal of their 
sender type by increasing the probability of retreating from a fight with 
individuals with larger badges (Fig. \ref{fig:branching}).
